### 2021-04-14 main.tex
Clean up the acknowledgements
Follow the recommendation from Hanka's email from 2021-04-14.

\todo{MS: zvazit, jestli nerozepsat zvlast Martin, zvlast Filip.
Pripadne se zeptat Hanky, jestli bychom nemeli nejak vypichnout
jen GACR.}

This work was supported by
the Czech Science Foundation project 20-06390Y,
the project RICAIP no. 857306 under the EU-H2020 programme,
and
the Grant Agency of the Czech Technical University in Prague, grant\\
no.~SGS20/215/OHK3/3T/37.

>>>>

This work was supported by
the Czech Science Foundation project no.~20-06390Y (JUNIOR grant),
the project RICAIP no. 857306 under the EU-H2020 programme,
and
the Grant Agency of the Czech Technical University in Prague, grant
no.~SGS20/215/OHK3/3T/37.
